Functory: A Distributed Computing Library \\ for Objective Caml \thanks{This research was partly supported by the French national project U3CAT (\emph{Unification of Critical C Code Analysis Techniques}, ANR-08-SEGI-021).}

### 2011-03-02 doc/tfp-2011/main.tex
updated (not yet complete) related work subsection [KK]

PlasmaMR~\cite{plasma} is an implementation of Google's MapReduce on a
distributed file system PlasmaFS. It is able to use PlasmaFS to its
advantage - the ability of the file system to handle large files and
query functions of the functions that implement data locality to
optimize network traffic. % However, Plasma
% MapReduce does not support fault tolerance.
The Disco
project~\cite{disco} is an implementation of Google's MapReduce in
Erlang~\cite{erlang}. Our library is not an impementation of Google's
MapReduce. A MapReduce implementation in \Ocaml\ is Yohann Padioleau's
MapReduce implementation in \Ocaml~\cite{poor-man-mapreduce}.  It is
built on top of OCamlMPI~\cite{ocamlMPI}, while our approach uses a
homemade protocol for message passing.  Currently, we have less
flexibility w.r.t. deployment of the user program than OCamlMPI; on
the other hand, we provide a more generic API together with fault
tolerance.

>>>>

PlasmaMR~\cite{plasma} is an implementation of Google's MapReduce on a
distributed file system PlasmaFS. It is able to use PlasmaFS to its
advantage - the ability of the file system to handle large files and
query functions of the functions that implement data locality to
optimize network traffic. However, Plasma MapReduce does not support
fault tolerance which is indespensible in any distributed computing
application. The Disco project~\cite{disco} is an implementation of
Google's MapReduce in Erlang~\cite{erlang}. Our library is not an
impementation of Google's MapReduce. A MapReduce implementation in
\Ocaml\ is Yohann Padioleau's MapReduce implementation in
\Ocaml~\cite{poor-man-mapreduce}.  It is built on top of
OCamlMPI~\cite{ocamlMPI}, while our approach uses a homemade protocol
for message passing.  Currently, we have less flexibility
w.r.t. deployment of the user program than OCamlMPI; on the other
hand, we provide a more generic API together with fault tolerance.
